---
author: "Eleanor Fewings"
output: html_document
---

# start_section  

```{r start_section}

# Time stamp
Sys.time()

# Clean up
rm(list=ls())

# Load libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(magrittr)
library(Seurat)
library(cowplot)
library(knitr)
library(DoMultiBarHeatmap)
library(tibble)
library(progeny)
library(pheatmap)
library(viridis)
library(tidyverse)

#Set working dir
setwd("C:/Users/ellie/Onedrive/Saez/Maurice_calc")

# Source functions
source("C:/Users/ellie/Onedrive/Saez/Maurice_calc/scripts/source.R")

```

MH6 - human kidney artery control 
MH7 - human kidney artery calcified 
MH11- human artery femoralis calcified
MH12- human artery femoralis control
MH13- human aorta calcified
MH14- human aorta control
MH15- human artery epigastrica calcified
MH16- human artery epigastrica control

#Read objects in
```{r read}

data <- readRDS("integrateddata_epigastra_p2.rds")

```

#Generate progeny scores
```{r}

#Run progeny on cases and controls
alldata <- runprog(data)

#Run progeny
data <- progeny(data, scale=FALSE, organism="Mouse", top=500, perm=1, return_assay = TRUE)
data <- ScaleData(data, assay = "progeny")

#Metadata
CellsClusters <- data@meta.data %>% 
  rownames_to_column('Cell') %>% 
  subset(select=c("cc", "celltype", "Cell", "cluster"))

colnames(CellsClusters) <- c("cc", "celltype1", "Cell", "cluster")

progeny_scores_df = as.data.frame(t(GetAssayData(data, slot = 'scale.data', assay = 'progeny'))) %>%
  rownames_to_column('Cell') %>%
  gather(Pathway, Activity, -Cell)
progeny_scores_df = inner_join(progeny_scores_df, CellsClusters)
progeny_scores_df$condition = progeny_scores_df$cc
progeny_scores_df$cell.type = paste(progeny_scores_df$celltype1, progeny_scores_df$cluster, sep="_")


# VSMC_0 cells
conditions = c('calcified', 'control')
celltype = "VSMC_0"
pathways = progeny_scores_df$Pathway %>% unique()

test.stats = compute_stats(df = progeny_scores_df, celltype = celltype, 
                           pathways = pathways, conditions = conditions, plot = TRUE)

#Plot output
test.stats$p

# VSMC_1 cells
conditions = c('calcified', 'control')
celltype = "VSMC_1"
pathways = progeny_scores_df$Pathway %>% unique()

test.stats = compute_stats(df = progeny_scores_df, celltype = celltype, 
                           pathways = pathways, conditions = conditions, plot = TRUE)

#Plot output
test.stats$p


#Replot all VSMC with only specific pathways
conditions = c('calcified', 'control')
celltype = c("VSMC_0", "VSMC_1")
pathways = c("Androgen", "EGFR", "JAK-STAT", "NFkB", "p53", "TNFa")

test.stats = compute_stats(df = progeny_scores_df, celltype = celltype, 
                           pathways = pathways, conditions = conditions, plot = TRUE)

#Plot output
test.stats$p



```

#Recreate response markers
```{r}
# Set case control identities
Idents(data) <- "cc"

# gather response genes per cluster
response.0 <- subset(data, subset= cluster == 0) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.1 <- subset(data, subset= cluster == 1) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.2 <- subset(data, subset= cluster == 2) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.3 <- subset(data, subset= cluster == 3) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.4 <- subset(data, subset= cluster == 4) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.5 <- subset(data, subset= cluster == 5) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.6 <- subset(data, subset= cluster == 6) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.7 <- subset(data, subset= cluster == 7) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.8 <- subset(data, subset= cluster == 8) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.9 <- subset(data, subset= cluster == 9) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.10 <- subset(data, subset= cluster == 10) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)

#Add cluster label
response.0$cluster <- "0"
response.1$cluster <- "1"
response.2$cluster <- "2"
response.3$cluster <- "3"
response.4$cluster <- "4"
response.5$cluster <- "5"
response.6$cluster <- "6"
response.7$cluster <- "7"
response.8$cluster <- "8"
response.9$cluster <- "9"
response.10$cluster <- "10"

#Add gene column
response.0$gene <- row.names(response.0)
response.1$gene <- row.names(response.1)
response.2$gene <- row.names(response.2)
response.3$gene <- row.names(response.3)
response.4$gene <- row.names(response.4)
response.5$gene <- row.names(response.5)
response.6$gene <- row.names(response.6)
response.7$gene <- row.names(response.7)
response.8$gene <- row.names(response.8)
response.9$gene <- row.names(response.9)
response.10$gene <- row.names(response.10)


#Cell types
label <- list("0"="VSMC",
     "1"="VSMC",
     "2"="Fibroblasts",
     "3"="Endothelial",
     "4"="Pericytes",
     "5"="Fibroblasts",
     "6"="Unknown",
     "7"="Endothelial",
     "8"="Pericytes",
     "9"="Fibroblasts",
     "10"="Immune")

```

#GSEA
```{r}

#Select genes to run analysis
bg.genes <- row.names(data)


#DE clusters
de.files <- list(response.0, response.1, response.2, response.3, response.4, response.5, response.6, response.7, response.8, response.9, response.10)

for (file in de.files){
  markers <- file[order(file$avg_log2FC, decreasing = TRUE),]
  rownames(markers) <- markers$gene
  
  # Get cell type
  clust <- unique(markers$cluster)
  cell.type <- label[names(label) == clust] %>% unlist() %>% str_replace("/", "_") %>% str_replace(" ", "_")
  cell.type <- paste(cell.type, paste0("cluster", clust), sep="_")
  outdir <- "GSEA/epigastra"
  dir.create(outdir)
  
  # GSEA
  stats <- markers$avg_log2FC
  names(stats) <- rownames(markers)
  stats <- stats[!is.na(stats)]
  file.prefix <- paste('healthy_vs_calcified_', cell.type, sep="") 
  
  # GO
  run_gsea(bg.genes = bg.genes, stats = stats, 
           category = 'C5', subcategory = 'BP',
           out.dir = outdir, plot.title = 'GO',
           file.prefix = file.prefix)
  
}



```

#Plotting specific markers
```{r}
#Create metadata
metadata <- data@meta.data

#Find gene names
BMPs <- bg.genes[grepl("BMP", bg.genes)]
MMPs <- bg.genes[grepl("MMP", bg.genes)]

#Create new marker sets
osteo <- c("RUNX2", "BMP2", "MSX2", "SPP1", "NOTCH1", "SOX9", "SP7", "TNFSF11", BMPs)
ecm <- c(MMPs, "COL1A1")
phos <- c("POU1F1", "SLC20A2", "ALPL", "ENPP1")
inflam <- c("IL6", "IL1B", "TNF")
others <- c("AGER", "S100A8", "S100A9", "S100A12")

#All
all.markers <- list(osteo=osteo, ecm=ecm, phos=phos, others=others)


#Clusters - VSMC, Fibroblasts and Pericytes
#clusters <- c(0,1,2,4,5,8,9)
clusters <- c(4,5,8,9)

for (clust in clusters){
  # Get cell type
  cell.type <- label[names(label) == clust] %>% unlist() %>% str_replace("/", "_") %>% str_replace(" ", "_")
  cell.type <- paste(cell.type, paste0("cluster", clust), sep="_")
  outdir <- "curated_geneset_analysis/epigastra"
  dir.create(outdir)
  
  # File names
  prefix.osteo <- paste(outdir, '/','healthy_vs_calcified_osteogenic_', cell.type, '.pdf', sep="") 
  prefix.ecm <- paste(outdir, '/', 'healthy_vs_calcified_ECM_', cell.type, '.pdf', sep="")
  prefix.phosphate <- paste(outdir, '/', 'healthy_vs_calcified_phostphate_', cell.type, '.pdf', sep="") 
  prefix.inflam <- paste(outdir, '/', 'healthy_vs_calcified_inflammation_', cell.type, '.pdf', sep="") 
  prefix.others <- paste(outdir, '/', 'healthy_vs_calcified_others_', cell.type, '.pdf', sep="")
  prefix.all <- paste(outdir, '/', 'healthy_vs_calcified_all_', cell.type, '.pdf', sep="")
  
  # Create osteo plot
  pdf(file = prefix.osteo, width = 10, height = 9)
  print(expr.plot(clust, osteo, "cc"))
  dev.off()
  
  # Create ecm plot
  pdf(file = prefix.ecm, width = 10, height = 9)
  print(expr.plot(clust, ecm, "cc"))
  dev.off()
  
  # Create phospho plot
  pdf(file = prefix.phosphate, width = 10, height = 9)
  print(expr.plot(clust, phos, "cc"))
  dev.off()
  
  # Create inflam plot
  pdf(file = prefix.inflam, width = 10, height = 9)
  print(expr.plot(clust, inflam, "cc"))
  dev.off()
  
  # Create others plot
  pdf(file = prefix.others, width = 10, height = 9)
  print(expr.plot(clust, others, "cc"))
  dev.off()
  
  # Create all plot
  pdf(file = prefix.all, width = 10, height = 9)
  print(gsea.expr.plot(clust, all.markers, "cc"))
  dev.off()
  
}

```

