---
author: "Eleanor Fewings"
output: html_document
---

# start_section  

```{r start_section}

# Time stamp
Sys.time()

# Clean up
rm(list=ls())

# Load libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(magrittr)
library(Seurat)
library(cowplot)
library(knitr)
library(DoMultiBarHeatmap)
library(DoubletFinder)

#Set working dir
setwd("C:/Users/ellie/Onedrive/Saez/Maurice_calc")

# Source functions
source("C:/Users/ellie/Onedrive/Saez/Maurice_calc/scripts/source.R")

```

MH6 - human kidney artery control 
MH7 - human kidney artery calcified 
MH11- human artery femoralis calcified
MH12- human artery femoralis control
MH13- human aorta calcified
MH14- human aorta control
MH15- human artery epigastrica calcified
MH16- human artery epigastrica control

#Read objects in
```{r read}
# Load
load("MH6/pipeline_output/s02_cluster_identity.Rdata")
#Rename
mh6 <- data
# Add sample label
mh6$sample <- "mh6"
# Add calc/control label
mh6$cc <- "control"
# Add location label
mh6$loc <- "kidney"
#Add cell type label to meta
mh6$celltype <- Idents(mh6)

# Load
load("MH7/pipeline_output/s02_cluster_identity.Rdata")
#Rename
mh7 <- data
# Add sample label
mh7$sample <- "mh7"
# Add calc/control label
mh7$cc <- "calcified"
# Add location label
mh7$loc <- "kidney"
#Add cell type label to meta
mh7$celltype <- Idents(mh7)

# Load
load("MH11/pipeline_output/s02_cluster_identity.Rdata")
#Rename
mh11 <- data
# Add sample label
mh11$sample <- "mh11"
# Add calc/control label
mh11$cc <- "calcified"
# Add location label
mh11$loc <- "femoralis"
#Add cell type label to meta
mh11$celltype <- Idents(mh11)

# Load
load("MH12/pipeline_output/s02_cluster_identity.Rdata")
#Rename
mh12 <- data
# Add sample label
mh12$sample <- "mh12"
# Add calc/control label
mh12$cc <- "control"
# Add location label
mh12$loc <- "femoralis"
#Add cell type label to meta
mh12$celltype <- Idents(mh12)

# Load
load("MH13/pipeline_output/s02_cluster_identity.Rdata")
#Rename
mh13 <- data
# Add sample label
mh13$sample <- "mh13"
# Add calc/control label
mh13$cc <- "calcified"
# Add location label
mh13$loc <- "aorta"
#Add cell type label to meta
mh13$celltype <- Idents(mh13)

# Load
load("MH14/pipeline_output/s02_cluster_identity.Rdata")
#Rename
mh14 <- data
# Add sample label
mh14$sample <- "mh14"
# Add calc/control label
mh14$cc <- "control"
# Add location label
mh14$loc <- "aorta"
#Add cell type label to meta
mh14$celltype <- Idents(mh14)

# Load
load("MH15/pipeline_output/s02_cluster_identity.Rdata")
#Rename
mh15 <- data
# Add sample label
mh15$sample <- "mh15"
# Add calc/control label
mh15$cc <- "calcified"
# Add location label
mh15$loc <- "epigastrica"
#Add cell type label to meta
mh15$celltype <- Idents(mh15)

# Load
load("MH16/pipeline_output/s02_cluster_identity.Rdata")
#Rename
mh16 <- data
# Add sample label
mh16$sample <- "mh16"
# Add calc/control label
mh16$cc <- "control"
# Add location label
mh16$loc <- "epigastrica"
#Add cell type label to meta
mh16$celltype <- Idents(mh16)

#Cleanup unnecassary objects
rm(clust, data, mt.patt, npcs, opt, pca, rdata, sample, script.dir, all.markers, ids, heat, initial.options, opt2, pca2)

obj <- c(mh6, mh7, mh11, mh12, mh13, mh14, mh15, mh16)

```

#Merge objects
```{r merge}

# select features that are repeatedly variable across datasets for integration
features <- SelectIntegrationFeatures(object.list = obj)

# Find anchors
anchors <- FindIntegrationAnchors(object.list = obj, anchor.features = features)

# Integrate data
data <- IntegrateData(anchorset = anchors, dims= 1:20)

#Checkpoint
#saveRDS(data, file = "integrateddata.rds")

#data <- readRDS("integrateddata.rds")

# Label assay
DefaultAssay(data) <- "integrated"

#Normalise data
data <- NormalizeData(data)

# Scale data on variable features (can be changed if requested)
data <- ScaleData(data, verbose = FALSE)

# Run PCA
data <- RunPCA(data, features = VariableFeatures(object = data), verbose = FALSE)

npcs <- get_npcs(seurat_object = data, create_plot = TRUE)

# Plot elbow plot for selection of principle components
npcs$plot

# Run UMAP
data <- RunUMAP(data, reduction = "pca", dims = 1:8, verbose = FALSE)


#Doublet finding (no ground truth)
sweep.res.list <- paramSweep_v3(data, PCs = 1:npcs$npcs, sct = TRUE)
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
bcmvn <- find.pK(sweep.stats)

## Homotypic doublet proportion estimation
homotypic.prop <- modelHomotypic(data@meta.data$seurat_clusters)           ## ex: annotations <- seu_kidney@meta.data$ClusteringResults
nExp_poi <- round(0.075*nrow(data@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

#Select pK
pK_sel <- as.numeric(as.character(bcmvn[which.max(bcmvn$BCmetric), "pK"]))

#Doublet finder
data <- doubletFinder_v3(data, PCs = 1:npcs$npcs, pN = 0.25, pK = pK_sel, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)

# Find neighbours
data <- FindNeighbors(data, reduction = "pca", dims = 1:8)
data <- FindClusters(data, resolution = 0.2)

```

#Visualise plots
```{r visualisation}

#Create short format of celltype (without allocation score)
data$celltypes1 <- data@meta.data$celltype %>% lapply( function(x) gsub(".*-","", x)) %>% lapply( function(x) gsub("\\(.*","", x)) %>% unlist()

#Plot old cell types to check integration
p1 <- DimPlot(data, reduction = "umap", group.by = "celltypes1")

# Plot cases vs controls
p2 <- DimPlot(data, reduction = "umap", group.by = "cc")

# Plot clusters
p3 <- DimPlot(data, reduction = "umap", label = TRUE)

# Create grid of plots
grid1 <- plot_grid(p1, p3)

grid1

# Create grid of plots
grid2 <- plot_grid(p2, p3)

grid2

```

#Label cell types
```{r cell types}

# Find markers for all clusters
clust.markers <- FindAllMarkers(data, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25, verbose = FALSE)

# Add cluster label
data$cluster <- Idents(data)

## List cell type markers
features_VSMC <- c("Myh11","Acta2","Tagln","Cnn1","Myocd","Vcl","Smtn","Ly6a") %>% toupper()
features_pericytes <- c("Cspg4","Pdgfrb","Colec11","Kcnj8","Abcc9","Vtn","Notch3") %>% toupper()
features_fibroblast <- c("Dcn","Lum","Pdgfra","Cd248","Col1a1","Apoe","Ogn","Postn") %>% toupper()
features_endothelial <- c("Cdh5","Pecam1","Kdr","Fabp4","Cd36") %>% toupper()
features_cellcycle <- c("Mki67","Ccnb2") %>% toupper()
features_immunecells <- c("Ptprc","Ms4a1","Cd79a","Lgals3","Ly6c1","Ncr1","Cd3e","S100a9","Cd209a","Fcgr1","Dab2","Hba-a1") %>% toupper()

allfeatures <- c(features_VSMC,
                 features_pericytes,
                 features_fibroblast,
                 features_endothelial,
                 features_cellcycle,
                 features_immunecells) %>% unique()

#Plot each set of features
FeaturePlot(data, feature = features_VSMC)
FeaturePlot(data, feature = features_pericytes)
FeaturePlot(data, feature = features_fibroblast)
FeaturePlot(data, feature = features_endothelial)
FeaturePlot(data, feature = features_cellcycle)
FeaturePlot(data, feature = features_immunecells)

#Plot vln of features
VlnPlot(data, feature = features_VSMC)
VlnPlot(data, feature = features_pericytes)
VlnPlot(data, feature = features_fibroblast)
VlnPlot(data, feature = features_endothelial)
VlnPlot(data, feature = features_cellcycle)
VlnPlot(data, feature = features_immunecells)

#Heatmap of clusters
DefaultAssay(data) <- "RNA"

data <- ScaleData(data, features=rownames(data), assay = "RNA")

DoHeatmap(data, features = allfeatures, assay = 'RNA', raster = FALSE, size = 3) + theme(text = element_text(size = 8))

DefaultAssay(data) <- "integrated"

types <- list("0"="VSMC",
     "1"="VSMC",
     "2"="Endothelial",
     "3"="Fibroblast",
     "4"="Immune",
     "5"="Fibroblast",
     "6"="Pericyte",
     "7"="unknown")

#Rename identities
data <- RenameIdents(data, types)
data$celltype <- Idents(data)

#Checkpoint 2
saveRDS(data, file = "integrateddata_p2.rds")

data <- readRDS("integrateddata_p2.rds")

```


#Identify differentially expressed genes
```{r DE}

# Set case control identities
Idents(data) <- "cc"

# Gather average expression
avg <- log1p(AverageExpression(data, verbose = FALSE)$RNA) %>% as.data.frame()

expr.plot <- ggplot(avg, aes(control, calcified)) + geom_point()

expr.plot

# Find case control markers
response <- FindMarkers(data, ident.1 = "calcified", ident.2 = "control", verbose = FALSE)

head(response, n = 15)

# Add average expression for cases
response <- merge(response, avg, by = "row.names", all.x=TRUE, all.y=FALSE)

colnames(response)[7:8] <- c("log1p_avg_calcified", "log1p_avg_controls")

#Select top genes
response.top <- response[order(response$avg_log2FC, decreasing = FALSE),][1:30,]
response.bottom <- response[order(response$avg_log2FC, decreasing = TRUE),][1:30,]

response.tb <- rbind(response.top, response.bottom)

#Plot heatmap of top genes
#DoHeatmap(data, features = response.tb$Row.names, assay = 'RNA', raster = FALSE, size = 3) + theme(text = element_text(size = 8))


# Plot (change to view specific features of interest)
#FeaturePlot(data, features = c("Mcpt1l1", "Ptgs2"), split.by = "cc", max.cutoff = 3, cols = c("grey", "red"))

```

#Identify differentially expressed genes per cluster
```{r DEC, error=TRUE}

# gather response genes per cluster
response.0 <- subset(data, subset= cluster == 0) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.1 <- subset(data, subset= cluster == 1) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.2 <- subset(data, subset= cluster == 2) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.3 <- subset(data, subset= cluster == 3) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.4 <- subset(data, subset= cluster == 4) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.5 <- subset(data, subset= cluster == 5) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.6 <- subset(data, subset= cluster == 6) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.7 <- subset(data, subset= cluster == 7) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)

# Gather average expression per cluster
avg.0 <- log1p(AverageExpression(subset(data, subset= cluster == 0), verbose = FALSE)$RNA)
avg.1 <- log1p(AverageExpression(subset(data, subset= cluster == 1), verbose = FALSE)$RNA)
avg.2 <- log1p(AverageExpression(subset(data, subset= cluster == 2), verbose = FALSE)$RNA)
avg.3 <- log1p(AverageExpression(subset(data, subset= cluster == 3), verbose = FALSE)$RNA)
avg.4 <- log1p(AverageExpression(subset(data, subset= cluster == 4), verbose = FALSE)$RNA)
avg.5 <- log1p(AverageExpression(subset(data, subset= cluster == 5), verbose = FALSE)$RNA)
avg.6 <- log1p(AverageExpression(subset(data, subset= cluster == 6), verbose = FALSE)$RNA)
avg.7 <- log1p(AverageExpression(subset(data, subset= cluster == 7), verbose = FALSE)$RNA)

#Add average expression for calcifieds
response.0 <- merge(response.0, avg.0, by = "row.names", all.x=TRUE, all.y=FALSE)
response.1 <- merge(response.1, avg.1, by = "row.names", all.x=TRUE, all.y=FALSE)
response.2 <- merge(response.2, avg.2, by = "row.names", all.x=TRUE, all.y=FALSE)
response.3 <- merge(response.3, avg.3, by = "row.names", all.x=TRUE, all.y=FALSE)
response.4 <- merge(response.4, avg.4, by = "row.names", all.x=TRUE, all.y=FALSE)
response.5 <- merge(response.5, avg.5, by = "row.names", all.x=TRUE, all.y=FALSE)
response.6 <- merge(response.6, avg.6, by = "row.names", all.x=TRUE, all.y=FALSE)
response.7 <- merge(response.7, avg.7, by = "row.names", all.x=TRUE, all.y=FALSE)

# Change column names
colnames(response.0)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.1)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.2)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.3)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.4)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.5)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.6)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.7)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")

```


#Save data
```{r save}

# Clean up
rm(avg, avg.0, avg.1, avg.2, avg.3, avg.4, avg.5, avg.6, avg.7, response.bottom, response.top)

# Save data
#save.image("results/integration.de.RData")

# Write csv
write.csv(response, "results/de.calcifiedcontrol.20210312.csv")

# Write csv per cluster
write.csv(response.0, "results/de.cluster0_calcifiedcontrol.20210312.csv")
write.csv(response.1, "results/de.cluster1_calcifiedcontrol.20210312.csv")
write.csv(response.2, "results/de.cluster2_calcifiedcontrol.20210312.csv")
write.csv(response.3, "results/de.cluster3_calcifiedcontrol.20210312.csv")
write.csv(response.4, "results/de.cluster4_calcifiedcontrol.20210312.csv")
write.csv(response.5, "results/de.cluster5_calcifiedcontrol.20210312.csv")
write.csv(response.6, "results/de.cluster6_calcifiedcontrol.20210312.csv")
write.csv(response.7, "results/de.cluster7_calcifiedcontrol.20210312.csv")


```

#Create heatmap of per celltype 
```{r}

#Select top significant genes on log fold change per cluster

top.0 <- response.0[order(response.0$p_val_adj, response.0$avg_log2FC),][1:10,]
top.1 <- response.1[order(response.1$p_val_adj, response.1$avg_log2FC),][1:10,]
top.2 <- response.2[order(response.2$p_val_adj, response.2$avg_log2FC),][1:10,]
top.3 <- response.3[order(response.3$p_val_adj, response.3$avg_log2FC),][1:10,]
top.4 <- response.4[order(response.4$p_val_adj, response.4$avg_log2FC),][1:10,]
top.5 <- response.5[order(response.5$p_val_adj, response.5$avg_log2FC),][1:10,]
top.6 <- response.6[order(response.6$p_val_adj, response.6$avg_log2FC),][1:10,]
top.7 <- response.7[order(response.7$p_val_adj, response.7$avg_log2FC),][1:10,]

#Bind into one table
all.top <- rbind(top.0, top.1, top.2, top.3, top.4, top.5, top.6, top.7)

all.top <- all.top[order(all.top$avg_log2FC, decreasing = TRUE),]

#Create annotation table
Idents(data) <- "celltype"

DoMultiBarHeatmap(object = data, features = all.top$Row.names, group.by = "cc", additional.group.by = "loc")


```

#Make per cluster heatmap
```{r}
#Create cluster-site identity
data$csite <- paste(data@meta.data$cc, data@meta.data$loc, sep="-")

#Set cc as identity
Idents(data) <- "cc"

#Cluster 0
c0 <- subset(data, subset= cluster == 0)

top.0 <- response.0[order(response.0$p_val_adj, response.0$avg_log2FC),][1:60,]

DoMultiBarHeatmap(object = c0, features = top.0$Row.names, group.by = "cc", additional.group.by = "loc")

#Cluster 1
c1 <- subset(data, subset= cluster == 1)

top.1 <- response.0[order(response.1$p_val_adj, response.1$avg_log2FC),][1:60,]

DoMultiBarHeatmap(object = c1, features = top.1$Row.names, group.by = "cc", additional.group.by = "loc")

#Cluster 2
c2 <- subset(data, subset= cluster == 2)

top.2 <- response.2[order(response.2$p_val_adj, response.2$avg_log2FC),][1:60,]

DoMultiBarHeatmap(object = c2, features = top.2$Row.names, group.by = "cc", additional.group.by = "loc")

#Cluster 3
c3 <- subset(data, subset= cluster == 3)

top.3 <- response.3[order(response.3$p_val_adj, response.3$avg_log2FC),][1:60,]

DoMultiBarHeatmap(object = c3, features = top.3$Row.names, group.by = "cc", additional.group.by = "loc")


#Cluster 4
c4 <- subset(data, subset= cluster == 4)

top.4 <- response.4[order(response.4$p_val_adj, response.4$avg_log2FC),][1:60,]

DoMultiBarHeatmap(object = c4, features = top.4$Row.names, group.by = "cc", additional.group.by = "loc")


#Cluster 5
c5 <- subset(data, subset= cluster == 5)

top.5 <- response.5[order(response.5$p_val_adj, response.5$avg_log2FC),][1:60,]

DoMultiBarHeatmap(object = c5, features = top.5$Row.names, group.by = "cc", additional.group.by = "loc")


#Cluster 6
c6 <- subset(data, subset= cluster == 6)

top.6 <- response.6[order(response.6$p_val_adj, response.6$avg_log2FC),][1:60,]

DoMultiBarHeatmap(object = c6, features = top.6$Row.names, group.by = "cc", additional.group.by = "loc")


#Cluster 7
c7 <- subset(data, subset= cluster == 7)

top.7 <- response.7[order(response.7$p_val_adj, response.7$avg_log2FC),][1:60,]

DoMultiBarHeatmap(object = c7, features = top.7$Row.names, group.by = "cc", additional.group.by = "loc")



```


