---
author: "Eleanor Fewings"
output: html_document
---

# start_section  

```{r start_section}

# Time stamp
Sys.time()

# Clean up
rm(list=ls())

# Load libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(magrittr)
library(Seurat)
library(cowplot)
library(knitr)
library(DoMultiBarHeatmap)
library(scDblFinder)

#Set working dir
setwd("C:/Users/ellie/Onedrive/Saez/Maurice_calc")

# Source functions
source("C:/Users/ellie/Onedrive/Saez/Maurice_calc/scripts/source.R")

```

MH6 - human kidney artery control 
MH7 - human kidney artery calcified 
MH11- human artery femoralis calcified
MH12- human artery femoralis control
MH13- human aorta calcified
MH14- human aorta control
MH15- human artery epigastrica calcified
MH16- human artery epigastrica control

#Read objects in
```{r read}
# Load
load("MH6/pipeline_output/s02_cluster_identity.Rdata")
#Rename
mh6 <- data
# Add sample label
mh6$sample <- "mh6"
# Add calc/control label
mh6$cc <- "control"
# Add location label
mh6$loc <- "kidney"
#Add cell type label to meta
mh6$celltype <- Idents(mh6)

#Doublet finding
doublets <- scDblFinder(sce = as.matrix(mh6@assays$RNA@counts), clusters = mh6@meta.data$seurat_clusters)
mh6$doublet_score <- doublets$scDblFinder.score
mh6$doublet <- doublets$scDblFinder.class

#Plot doublets
DimPlot(mh6, reduction = "umap", group.by = "seurat_clusters")
DimPlot(mh6, reduction = "umap", group.by = "doublet")

#Remove doublets
mh6 <- subset(mh6, subset= doublet == "singlet")

# Load
load("MH7/pipeline_output/s02_cluster_identity.Rdata")
#Rename
mh7 <- data
# Add sample label
mh7$sample <- "mh7"
# Add calc/control label
mh7$cc <- "calcified"
# Add location label
mh7$loc <- "kidney"
#Add cell type label to meta
mh7$celltype <- Idents(mh7)

#Doublet finding
doublets <- scDblFinder(sce = as.matrix(mh7@assays$RNA@counts), clusters = mh7@meta.data$seurat_clusters)
mh7$doublet_score <- doublets$scDblFinder.score
mh7$doublet <- doublets$scDblFinder.class

#Plot doublets
DimPlot(mh7, reduction = "umap", group.by = "seurat_clusters")
DimPlot(mh7, reduction = "umap", group.by = "doublet")

#Remove doublets
mh7 <- subset(mh7, subset= doublet == "singlet")

#Cleanup unnecassary objects
rm(clust, data, mt.patt, npcs, opt, pca, rdata, sample, script.dir, all.markers, ids, heat, initial.options, opt2, pca2, doublets)

obj <- c(mh6, mh7)

```

#Markers to integrate
```{r}
## List cell type markers
features_VSMC <- c("Myh11","Acta2","Tagln","Cnn1","Myocd","Vcl","Smtn","Ly6a") %>% toupper()
features_pericytes <- c("Cspg4","Pdgfrb","Colec11","Kcnj8","Abcc9","Vtn","Notch3") %>% toupper()
features_fibroblast <- c("Dcn","Lum","Pdgfra","Cd248","Col1a1","Apoe","Ogn","Postn") %>% toupper()
features_endothelial <- c("Cdh5","Pecam1","Kdr","Fabp4","Cd36") %>% toupper()
features_cellcycle <- c("Mki67","Ccnb2") %>% toupper()
features_immunecells <- c("Ptprc","Ms4a1","Cd79a","Lgals3","Ly6c1","Ncr1","Cd3e","S100a9","Cd209a","Fcgr1","Dab2","Hba-a1", "Cd68", "Ighm") %>% toupper()

allfeatures <- c(features_VSMC,
                 features_pericytes,
                 features_fibroblast,
                 features_endothelial,
                 features_cellcycle,
                 features_immunecells) %>% unique()
```


#Merge objects
```{r merge}

# select features that are repeatedly variable across datasets for integration
features <- SelectIntegrationFeatures(object.list = obj)

# Find anchors
anchors <- FindIntegrationAnchors(object.list = obj, anchor.features = c(features, allfeatures))

# Integrate data
data <- IntegrateData(anchorset = anchors, dims= 1:20, features.to.integrate = c(features, allfeatures))

#Checkpoint
#saveRDS(data, file = "integrateddata.kidney.rds")

#data <- readRDS("integrateddata.kidney.rds")

# Label assay
DefaultAssay(data) <- "integrated"

# Scale data on variable features (can be changed if requested)
data <- ScaleData(data, verbose = FALSE, features=rownames(data))

# Run PCA
data <- RunPCA(data, features = VariableFeatures(object = data), verbose = FALSE)

npcs <- get_npcs(seurat_object = data, create_plot = TRUE)

# Plot elbow plot for selection of principle components
npcs$plot

# Run UMAP
data <- RunUMAP(data, reduction = "pca", dims = 1:10, verbose = FALSE)

# Find neighbours
data <- FindNeighbors(data, reduction = "pca", dims = 1:10)
data <- FindClusters(data, resolution = 0.2)


```

#Visualise plots
```{r visualisation}

#Create short format of celltype (without allocation score)
data$celltypes1 <- data@meta.data$celltype %>% lapply( function(x) gsub(".*-","", x)) %>% lapply( function(x) gsub("\\(.*","", x)) %>% unlist()

#Plot old cell types to check integration
p1 <- DimPlot(data, reduction = "umap", group.by = "celltypes1")

DimPlot(data, reduction = "umap", group.by = "celltypes1")

# Plot cases vs controls
p2 <- DimPlot(data, reduction = "umap", group.by = "cc")

# Plot clusters
p3 <- DimPlot(data, reduction = "umap", label = TRUE)

# Create grid of plots
grid1 <- plot_grid(p1, p3)

grid1

# Create grid of plots
grid2 <- plot_grid(p2, p3)

grid2

```

#Label cell types
```{r cell types}

# Find markers for all clusters
clust.markers <- FindAllMarkers(data, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25, verbose = FALSE)
top10 <- clust.markers %>% group_by(cluster) %>% top_n(10, avg_log2FC)

# Add cluster label
data$cluster <- Idents(data)

## List cell type markers
features_VSMC <- c("Myh11","Acta2","Tagln","Cnn1","Myocd","Vcl","Smtn","Ly6a") %>% toupper()
features_pericytes <- c("Cspg4","Pdgfrb","Colec11","Kcnj8","Abcc9","Vtn","Notch3") %>% toupper()
features_fibroblast <- c("Dcn","Lum","Pdgfra","Cd248","Col1a1","Apoe","Ogn","Postn") %>% toupper()
features_endothelial <- c("Cdh5","Pecam1","Kdr","Fabp4","Cd36") %>% toupper()
features_cellcycle <- c("Mki67","Ccnb2") %>% toupper()
features_immunecells <- c("Ptprc","Ms4a1","Cd79a","Lgals3","Ly6c1","Ncr1","Cd3e","S100a9","Cd209a","Fcgr1","Dab2","Hba-a1", "Cd68", "Ighm") %>% toupper()

allfeatures <- c(features_VSMC,
                 features_pericytes,
                 features_fibroblast,
                 features_endothelial,
                 features_cellcycle,
                 features_immunecells) %>% unique()

#Plot each set of features
FeaturePlot(data, feature = features_VSMC)
FeaturePlot(data, feature = features_pericytes)
FeaturePlot(data, feature = features_fibroblast)
FeaturePlot(data, feature = features_endothelial)
FeaturePlot(data, feature = features_cellcycle)
FeaturePlot(data, feature = features_immunecells)

#Plot vln of features
VlnPlot(data, feature = features_VSMC)
VlnPlot(data, feature = features_pericytes)
VlnPlot(data, feature = features_fibroblast)
VlnPlot(data, feature = features_endothelial)
VlnPlot(data, feature = features_cellcycle)
VlnPlot(data, feature = features_immunecells)

#Heatmap of clusters
DefaultAssay(data) <- "RNA"

data <- ScaleData(data, features=rownames(data), assay = "RNA")

DoHeatmap(data, features = top10$gene, raster = FALSE, size = 3) + theme(text = element_text(size = 8))

#Heatmap of proported immune cell markers
data.immune <- subset(data, subset= seurat_clusters %in% c("7", "10", "12"))

data.immune$cluster <- factor(data.immune@meta.data$seurat_clusters, levels=unique(data.immune@meta.data$seurat_clusters))

markers.immune <- FindAllMarkers(data.immune, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25, verbose = FALSE)

top.immune <- markers.immune %>% filter(p_val_adj < 0.05) %>% group_by(cluster) %>% top_n(-15, p_val_adj) %>% top_n(15, avg_log2FC)

DoHeatmap(object = data.immune, features = top.immune$gene, group.by = "cluster")

DoMultiBarHeatmap(object = data.immune, features = top.immune$gene, group.by = "cluster", additional.group.by = "cc")

#Label celltypes

#DefaultAssay(data) <- "integrated"

types <- list("0"="VSMC",
     "1"="VSMC",
     "2"="Fibroblasts",
     "3"="Endothelial",
     "4"="Fibroblasts",
     "5"="VSMC",
     "6"="Endothelial",
     "7"="Immune",
     "8"="Unknown",
     "9"="Pericytes",
     "10"="T-cells",
     "11"="Endothelial",
     "12"="Granulocytes")

#Rename identities
data <- RenameIdents(data, types)
data$celltype <- Idents(data)

#Checkpoint 2
#saveRDS(data, file = "integrateddata_kidney_p2.rds")

#data <- readRDS("integrateddata_kidney_p2.rds")

```

#Check proportion of clusters in calcified and controls
```{r prop}

meta.sum <- data@meta.data %>% 
  group_by(seurat_clusters) %>% 
  mutate(count.calcified=sum(cc == "calcified"), count.cont=sum(cc == "control")) %>% 
  subset(select=c(seurat_clusters, count.calcified, count.cont)) %>% 
  unique()


meta.sum <- meta.sum %>% gather(cc, counts, 2:3)

ggplot(meta.sum, aes(x=seurat_clusters, y=counts, fill=cc)) +
  geom_bar(stat="identity", position = "dodge")

```



#Identify differentially expressed genes
```{r DE}

# Set case control identities
Idents(data) <- "cc"

# Gather average expression
avg <- log1p(AverageExpression(data, verbose = FALSE)$RNA) %>% as.data.frame()

expr.plot <- ggplot(avg, aes(control, calcified)) + geom_point()

expr.plot

# Find case control markers
response <- FindMarkers(data, ident.1 = "calcified", ident.2 = "control", verbose = FALSE)

head(response, n = 15)

# Add average expression for cases
response <- merge(response, avg, by = "row.names", all.x=TRUE, all.y=FALSE)

colnames(response)[7:8] <- c("log1p_avg_calcified", "log1p_avg_controls")

#Select top genes
response.top <- response[order(response$avg_log2FC, decreasing = FALSE),][1:30,]
response.bottom <- response[order(response$avg_log2FC, decreasing = TRUE),][1:30,]

response.tb <- rbind(response.top, response.bottom)

#Plot heatmap of top genes
DoHeatmap(data, features = response.tb$Row.names, assay = 'RNA', raster = FALSE, size = 3) + theme(text = element_text(size = 8))


# Plot (change to view specific features of interest)
#FeaturePlot(data, features = c("Mcpt1l1", "Ptgs2"), split.by = "cc", max.cutoff = 3, cols = c("grey", "red"))

```

#Identify differentially expressed genes per cluster
```{r DEC, error=TRUE}

# gather response genes per cluster
response.0 <- subset(data, subset= cluster == 0) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.1 <- subset(data, subset= cluster == 1) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.2 <- subset(data, subset= cluster == 2) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.3 <- subset(data, subset= cluster == 3) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.4 <- subset(data, subset= cluster == 4) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.5 <- subset(data, subset= cluster == 5) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.6 <- subset(data, subset= cluster == 6) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.7 <- subset(data, subset= cluster == 7) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.8 <- subset(data, subset= cluster == 8) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.9 <- subset(data, subset= cluster == 9) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.10 <- subset(data, subset= cluster == 10) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.11 <- subset(data, subset= cluster == 11) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)
response.12 <- subset(data, subset= cluster == 12) %>% FindMarkers(ident.1 = "calcified", ident.2 = "control", verbose = FALSE)

# Gather average expression per cluster
avg.0 <- log1p(AverageExpression(subset(data, subset= cluster == 0), verbose = FALSE)$RNA)
avg.1 <- log1p(AverageExpression(subset(data, subset= cluster == 1), verbose = FALSE)$RNA)
avg.2 <- log1p(AverageExpression(subset(data, subset= cluster == 2), verbose = FALSE)$RNA)
avg.3 <- log1p(AverageExpression(subset(data, subset= cluster == 3), verbose = FALSE)$RNA)
avg.4 <- log1p(AverageExpression(subset(data, subset= cluster == 4), verbose = FALSE)$RNA)
avg.5 <- log1p(AverageExpression(subset(data, subset= cluster == 5), verbose = FALSE)$RNA)
avg.6 <- log1p(AverageExpression(subset(data, subset= cluster == 6), verbose = FALSE)$RNA)
avg.7 <- log1p(AverageExpression(subset(data, subset= cluster == 7), verbose = FALSE)$RNA)
avg.8 <- log1p(AverageExpression(subset(data, subset= cluster == 8), verbose = FALSE)$RNA)
avg.9 <- log1p(AverageExpression(subset(data, subset= cluster == 9), verbose = FALSE)$RNA)
avg.10 <- log1p(AverageExpression(subset(data, subset= cluster == 10), verbose = FALSE)$RNA)
avg.11 <- log1p(AverageExpression(subset(data, subset= cluster == 11), verbose = FALSE)$RNA)
avg.12 <- log1p(AverageExpression(subset(data, subset= cluster == 12), verbose = FALSE)$RNA)

#Add average expression for calcifieds
response.0 <- merge(response.0, avg.0, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.1 <- merge(response.1, avg.1, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.2 <- merge(response.2, avg.2, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.3 <- merge(response.3, avg.3, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.4 <- merge(response.4, avg.4, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.5 <- merge(response.5, avg.5, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.6 <- merge(response.6, avg.6, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.7 <- merge(response.7, avg.7, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.8 <- merge(response.8, avg.8, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.9 <- merge(response.9, avg.9, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.10 <- merge(response.10, avg.10, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.11 <- merge(response.11, avg.11, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)
response.12 <- merge(response.12, avg.12, by = "row.names", all.x=TRUE, all.y=FALSE) %>% filter(p_val_adj < 0.05)

# Change column names
colnames(response.0)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.1)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.2)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.3)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.4)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.5)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.6)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.7)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.8)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.9)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.10)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.11)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")
colnames(response.12)[7:8] <- c("log1p_avg_calcifieds", "log1p_avg_controls")

```


#Save data
```{r save}

# Clean up
rm(avg, avg.0, avg.1, avg.2, avg.3, avg.4, avg.5, avg.6, avg.7, avg.8, avg.9, avg.10, avg.11, avg.12, response.bottom, response.top)

# Save data
#save.image("results/integration.de.RData")

# Write csv
write.csv(response, "results/kidney/kidney.de.calcifiedcontrol.20210412.csv")

# Write csv per cluster
write.csv(response.0, "results/kidney/de.cluster0_calcifiedcontrol.20210412.csv")
write.csv(response.1, "results/kidney/de.cluster1_calcifiedcontrol.20210412.csv")
write.csv(response.2, "results/kidney/de.cluster2_calcifiedcontrol.20210412.csv")
write.csv(response.3, "results/kidney/de.cluster3_calcifiedcontrol.20210412.csv")
write.csv(response.4, "results/kidney/de.cluster4_calcifiedcontrol.20210412.csv")
write.csv(response.5, "results/kidney/de.cluster5_calcifiedcontrol.20210412.csv")
write.csv(response.6, "results/kidney/de.cluster6_calcifiedcontrol.20210412.csv")
write.csv(response.7, "results/kidney/de.cluster7_calcifiedcontrol.20210412.csv")
write.csv(response.8, "results/kidney/de.cluster8_calcifiedcontrol.20210412.csv")
write.csv(response.9, "results/kidney/de.cluster9_calcifiedcontrol.20210412.csv")
write.csv(response.10, "results/kidney/de.cluster10_calcifiedcontrol.20210412.csv")
write.csv(response.11, "results/kidney/de.cluster11_calcifiedcontrol.20210412.csv")
write.csv(response.12, "results/kidney/de.cluster12_calcifiedcontrol.20210412.csv")


```

#Create heatmap of per celltype 
```{r}

#Select top significant genes on log fold change per cluster

top.0 <- response.0[order(response.0$avg_log2FC),][1:10,]
top.1 <- response.1[order(response.1$avg_log2FC),][1:10,]
top.2 <- response.2[order(response.2$avg_log2FC),][1:10,]
top.3 <- response.3[order(response.3$avg_log2FC),][1:10,]
top.4 <- response.4[order(response.4$avg_log2FC),][1:10,]
top.5 <- response.5[order(response.5$avg_log2FC),][1:10,]
top.6 <- response.6[order(response.6$avg_log2FC),][1:10,]
top.7 <- response.7[order(response.7$avg_log2FC),][1:10,]
top.8 <- response.8[order(response.8$avg_log2FC),][1:10,]
top.9 <- response.9[order(response.9$avg_log2FC),][1:10,]
top.10 <- response.10[order(response.10$avg_log2FC),][1:10,]
top.11 <- response.11[order(response.11$avg_log2FC),][1:10,]
top.12 <- response.12[order(response.12$avg_log2FC),][1:10,]

#Bind into one table
all.top <- rbind(top.0, top.1, top.2, top.3, top.4, top.5, top.6, top.7, top.8, top.9, top.10, top.11, top.12)

all.top <- all.top[order(all.top$avg_log2FC, decreasing = TRUE),]

#Create annotation table
Idents(data) <- "celltype"

data$cluster.fct <- factor(as.character(data@meta.data$seurat_clusters), levels=levels(data@meta.data$seurat_clusters))

DoMultiBarHeatmap(object = data, features = all.top$Row.names, group.by = "cc", additional.group.by = "cluster.fct")


```

#Make per cluster heatmap
```{r}
#Create cluster-site identity
data$csite <- paste(data@meta.data$cc, data@meta.data$loc, sep="-")

#Set cc as identity
Idents(data) <- "cc"

#Cluster 0
c0 <- subset(data, subset= cluster == 0)

top.0 <- response.0[order(response.0$avg_log2FC),][1:30,]
bot.0 <- response.0[order(response.0$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c0, features = unique(c(top.0$Row.names, bot.0$Row.names)), group.by = "cc", additional.group.by = "celltype")

#Cluster 1
c1 <- subset(data, subset= cluster == 1)

top.1 <- response.1[order(response.1$avg_log2FC),][1:30,]
bot.1 <- response.1[order(response.1$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c1, features = unique(c(top.1$Row.names, bot.1$Row.names)), group.by = "cc", additional.group.by = "celltype")

#Cluster 2
c2 <- subset(data, subset= cluster == 2)

top.2 <- response.2[order(response.2$avg_log2FC),][1:30,]
bot.2 <- response.2[order(response.2$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c2, features = unique(c(top.2$Row.names, bot.2$Row.names)), group.by = "cc", additional.group.by = "celltype")

#Cluster 3
c3 <- subset(data, subset= cluster == 3)

top.3 <- response.3[order(response.3$avg_log2FC),][1:30,]
bot.3 <- response.3[order(response.3$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c3, features = unique(c(top.3$Row.names, bot.3$Row.names)), group.by = "cc", additional.group.by = "celltype")


#Cluster 4
c4 <- subset(data, subset= cluster == 4)

top.4 <- response.4[order(response.4$avg_log2FC),][1:30,]
bot.4 <- response.4[order(response.4$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c4, features = unique(c(top.4$Row.names, bot.4$Row.names)), group.by = "cc", additional.group.by = "celltype")


#Cluster 5
c5 <- subset(data, subset= cluster == 5)

top.5 <- response.5[order(response.5$avg_log2FC),][1:30,]
bot.5 <- response.5[order(response.5$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c5, features = unique(c(top.5$Row.names, bot.5$Row.names)), group.by = "cc", additional.group.by = "celltype")


#Cluster 6
c6 <- subset(data, subset= cluster == 6)

top.6 <- response.6[order(response.6$avg_log2FC),][1:30,]
bot.6 <- response.6[order(response.6$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c6, features = unique(c(top.6$Row.names, bot.6$Row.names)), group.by = "cc", additional.group.by = "celltype")


#Cluster 7
c7 <- subset(data, subset= cluster == 7)

top.7 <- response.7[order(response.7$avg_log2FC),][1:30,]
bot.7 <- response.7[order(response.7$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c7, features = unique(c(top.7$Row.names, bot.7$Row.names)), group.by = "cc", additional.group.by = "celltype")


#Cluster 8
c8 <- subset(data, subset= cluster == 8)

top.8 <- response.8[order(response.8$avg_log2FC),][1:30,]
bot.8 <- response.8[order(response.8$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c8, features = unique(c(top.8$Row.names, bot.8$Row.names)), group.by = "cc", additional.group.by = "celltype")


#Cluster 9
c9 <- subset(data, subset= cluster == 9)

top.9 <- response.9[order(response.9$avg_log2FC),][1:30,]
bot.9 <- response.9[order(response.9$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c9, features = unique(c(top.9$Row.names, bot.9$Row.names)), group.by = "cc", additional.group.by = "celltype")


#Cluster 10
c10 <- subset(data, subset= cluster == 10)

top.10 <- response.10[order(response.10$avg_log2FC),][1:30,]
bot.10 <- response.10[order(response.10$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c10, features = unique(c(top.10$Row.names, bot.10$Row.names)), group.by = "cc", additional.group.by = "celltype")

#Cluster 11
c11 <- subset(data, subset= cluster == 11)

top.11 <- response.11[order(response.11$avg_log2FC),][1:30,]
bot.11 <- response.11[order(response.11$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c11, features = unique(c(top.11$Row.names, bot.11$Row.names)), group.by = "cc", additional.group.by = "celltype")

#Cluster 12
c12 <- subset(data, subset= cluster == 12)

top.12 <- response.12[order(response.12$avg_log2FC),][1:30,]
bot.12 <- response.12[order(response.12$avg_log2FC, decreasing = TRUE),][1:30,]

DoMultiBarHeatmap(object = c12, features = unique(c(top.12$Row.names, bot.12$Row.names)), group.by = "cc", additional.group.by = "celltype")


```


